Different rules for binocular combination of luminance flicker in cortical and subcortical pathways

### 2023-06-24 manuscript.Rmd
Added reference to Baitch & Levi 1988

In the steady-state literature, one hallmark of a nonlinear system that pools inputs is the presence of intermodulation responses at the sums and differences of the fundamental flicker frequencies [@Tsai2012]. In Figure \@ref(fig:IMfig) we plot the amplitude spectra of conditions from Experiment 1 in which the two eyes were stimulated at different frequencies (2Hz and 1.6Hz) but at the same contrast (48\%; these correspond to the binocular cross and dichoptic cross conditions in Figures \@ref(fig:pupildata)d,e and \@ref(fig:EEGdata)d,e). Figure \@ref(fig:IMfig)a reveals a strong intermodulation difference response at 0.4Hz (red dashed line), and Figure \@ref(fig:IMfig)b reveals an intermodulation sum response at 3.6Hz (red dashed line). It seems likely that the absence of a sum response for pupillometry data, and of a difference responses for the EEG data, is a consequence of the temporal constraints of these methods. The presence of  intermodulation terms is predicted by nonlinear gain control models of the type considered here [@Tsai2012; @Baker2017], and indicates that the processing of monocular flicker signals is not fully linear prior to the point at which they are combined across the eyes. Indeed, our model architecture [@Meese2006] makes specific predictions about the location of interocular suppression - it impacts before binocular combination, consistent with results from primate physiology [@Dougherty2019].

>>>>

In the steady-state literature, one hallmark of a nonlinear system that pools inputs is the presence of intermodulation responses at the sums and differences of the fundamental flicker frequencies [@Baitch1988; @Tsai2012]. In Figure \@ref(fig:IMfig) we plot the amplitude spectra of conditions from Experiment 1 in which the two eyes were stimulated at different frequencies (2Hz and 1.6Hz) but at the same contrast (48\%; these correspond to the binocular cross and dichoptic cross conditions in Figures \@ref(fig:pupildata)d,e and \@ref(fig:EEGdata)d,e). Figure \@ref(fig:IMfig)a reveals a strong intermodulation difference response at 0.4Hz (red dashed line), and Figure \@ref(fig:IMfig)b reveals an intermodulation sum response at 3.6Hz (red dashed line). It seems likely that the absence of a sum response for pupillometry data, and of a difference responses for the EEG data, is a consequence of the temporal constraints of these methods. The presence of  intermodulation terms is predicted by nonlinear gain control models of the type considered here [@Tsai2012; @Baker2017], and indicates that the processing of monocular flicker signals is not fully linear prior to the point at which they are combined across the eyes. Indeed, our model architecture [@Meese2006] makes specific predictions about the location of interocular suppression - it impacts before binocular combination, consistent with results from primate physiology [@Dougherty2019].
